TacticToe: Learning the Game of Tactics

### 2018-02-14 tactictoe_jv.tex
example wip

To conclude, we also demonstrate the capabilities of \tactictoe on two goals 
that do not have a proof in \holfour.

The first goal, in Example~, states that the set of 
natural numbers is countable. \tactictoe starts from the definition of 
countability and injection then instantiate the result with the trivial 
injection and finalize the proof using the \metis. Here,
\tactictoe is able to find an instantiation for an existential quantifier 
because it is a common one. If a more complicated term was needed, \tactictoe 
would try to find an alternative proof that do not rely on an original
instantiation. This weakness could be mitigated by the introduction of term 
prediction in a future version of \tactictoe.

\begin{example}
\begin{lstlisting}[language=SMLSmall]
countable (UNIV:num set)
let fun RWTAC thms = SRW_TAC [] thms in
  RWTAC [countable_def, INJ_DEF] THEN Q.EXISTS_TAC `\\x.x` THEN METIS_TAC []
end
\end{lstlisting}
\end{example}

The second goal, in Example~, \todoi{TG to RK: I am not sure what the count 
constant is doing.}

>>>>

To conclude, we also demonstrate the capabilities of \tactictoe on a goal
that did not have a proof in \holfour.

\todoi{commented out because the theorem exists in hoL4}.
%The first goal, in Example~, states that the set of 
%natural numbers is countable. \tactictoe starts from the definition of 
%countability and injection then instantiate the result with the trivial 
%injection and finalize the proof using the \metis. Here,
%\tactictoe is able to find an instantiation for an existential quantifier 
%because it is a common one. If a more complicated term was needed, \tactictoe 
%would try to find an alternative proof that do not rely on an original
%instantiation. This weakness could be mitigated by the introduction of term 
%prediction in a future version of \tactictoe.

%\begin{example}
%\begin{lstlisting}[language=SMLSmall]
%countable (UNIV:num set)
%let fun RWTAC thms = SRW_TAC [] thms in
%  RWTAC [countable_def, INJ_DEF] THEN Q.EXISTS_TAC `\\x.x` THEN METIS_TAC []
%end
%\end{lstlisting}
%\end{example}

In Example~, \todoi{TG to RK: I am not sure what the count 
constant is doing.}
